---
output:
  md_document:
    variant: markdown
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Presenter mode

Speaker notes can be added like this to any section:

```markup
<aside class="notes">
* These are some *presenter notes*.
* You can use `markdown` in those notes as well.
* Courtesy of the [reveal.js](https://revealjs.com/) framework.
</aside>
```
Press `S` to bring up a window in presenter mode.

<aside class="notes">
* These are some *presenter notes*.
* You can use `markdown` in those notes as well.
* Courtesy of the [reveal.js](https://revealjs.com/) framework.
</aside>


# In the morning

## Getting up

- Turn **off** alarm
- Get out of bed

## Breakfast 

- Eat eggs
- Drink coffee

# In the evening

## Dinner

- Eat spaghetti
- Drink wine

## Going to sleep

- Get in bed
- Count sheep

# Pretty code highlighting

## Some code from the revealjs presentation

```javascript
function linkify( selector ) {
  if( supports3DTransforms ) {

    var nodes = document.querySelectorAll( selector );

    for( var i = 0, len = nodes.length; i &lt; len; i++ ) {
      var node = nodes[i];

      if( !node.className ) {
        node.className += ' roll';
      }
    }
  }
}
```

# Inclusion of R code

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```
